---
title: "Special Teams Positions"
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(readxl)
library(tidyverse)
library(scales)
library(plotly)
```

```{r, out.width="200%"}
read_rds("NFL_Special_plot.rds")
```

The **Special Teams** only has 3 positions which are essential for the team to succeed. The reason why they are the lowest paid out of the three category is because they play for a short amount of time of the game. **Long snapper** is the lowest paid position in all positions, the average is less than a million. If you like to see each player's salary by year you can interact with the plot below.

```{r}
NFL_interactive_plot <- read_excel("NFL12.xlsx")
options(scipen = 100)
NFL_interactive_plot$Position = factor(NFL_interactive_plot$Position, labels = c("Kicker", "Punter", "Long Snapper"), levels = c("K", "P", "LS"))
NFL_interactive_plot <- NFL_interactive_plot |>
  ggplot(aes(x = Year, y = Salary, col = Position, text = paste("Year: ", Year, "\nSalary:", Salary, "\nPosition:", Position, "\nPlayer:", Player))) + 
  geom_jitter(size = 2) + 
  scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6)) + 
  labs(title = "Special Team Player Interactive Plot",
       y = "Salary", fill = "Position",
       caption = "Source: Sportrac")

NFL_interactive_plot = ggplotly(NFL_interactive_plot, tooltip = "text")
NFL_interactive_plot
```

